\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
24 Approx covs: added comma
3.1 Simulations

    \subsection{Approximate covariances}\label{ssec:theory.approx}
      When presenting our results in Section \ref{sec:results}, we will compare the true covariance matrix, estimated from a large number of Gaussian simulations, with the analytical covariance estimated under different approximations. In descending order of complexity, these are:
      \begin{enumerate}
        \item The narrow-kernel approximation (labelled {\bf NKA} here), described in the previous sections. This approximation assumes that the support of the harmonic-space masks (represented by the mode-coupling coefficients in e.g. Eq. \ref{eq:mcms}) is small compared to the variation of the true power spectrum with $\ell$. Additionally, it neglects all derivatives of the sky mask when accounting for the spin nature of the fields involved.
        \item The {\bf spin-0} approximation corresponds to a simplified version of the NKA in which the spin nature of all fields involved is completely ignored, and all fields, including the $E$- and $B$-mode components of a spin-2 field, are treated as spin-0 quantities.
        \item The mode-counting approximation (labelled {\bf MC} here), commonly known as the {\sl Knox formula} \cite{1995PhRvD..52.4307K}, which applies the result found for full-sky observations (Eq. \ref{eq:cov_naive}) to masked fields corrected by an overall factor that accounts to the loss of modes due to the sky mask. In this case, the covariance is simply given by:
        \begin{equation}\label{eq:cov_naive_bpw}
          {\rm Cov}\left(C^{ab}_q,C^{cd}_{q'}\right)=\delta^K_{qq'}\frac{C^{ad}_qC^{bc}_q+C^{ac}_qC^{bd}_q}{(2\ell_q+1)\,f_{\rm sky}\,N_q},
        \end{equation}
        where $\ell_q$ is the mean multipole in the $q$-th bandpower, $N_q$ is the number of multipoles assigned to it, and $f_{\rm sky}$ is the available sky fraction.
      \end{enumerate}

@@

      We consider the case of auto- and cross-correlations between all fields in two redshift bins, with redshift distributions modelled as Gaussians with width $\sigma_z=0.13$ centered around redshifts $0.75$ and $0.95$, with number densities $n_\Omega=7.5\,{\rm arcmin}^{-2}$. The corresponding redshift distributions $p_z(z)$ are shown in Figure \ref{fig:pz}. For simplicity we use a constant bias $b(z)=1$. For these specifications, we generate signal power spectra using the Core Cosmology Library ({\tt CCL} \cite{2019ApJS..242....2C}) for cosmological parameters $(\Omega_c,\Omega_b,h,A_s,n_s)=(0.27,0.045,0.67,2.1\times10^{-9},0.96)$. The resulting non-zero signal and noise power spectra are shown in Fig. \ref{fig:cl-2bins}.

@@

      We have also explored the impact of the presence of sky contaminants on the estimate of the covariance matrix. As described in \cite{2019MNRAS.484.4127A}, the presence of a small contamination from observational systematics in the data can be accounted for through a technique known as {\sl mode deprojection} \cite{1992ApJ...398..169R,2004PhRvD..69l3003S,2017MNRAS.465.1847E}. In this method, the contamination is modeled as a linear contribution at the map level from contaminants with a known template. Mode deprojection then consists on projecting the data onto the subspace of modes that are perpendicular to those templates, effectively removing all modes from the map that ``look like'' any of the contaminants. This removal of modes has been shown to provide unbiased estimates of the power spectrum, however it could potentially affect the power spectrum uncertainties due to the loss of statistical power. To study this effect, we have also generated contaminant maps of two types:
      \begin{itemize}
        \item {\bf Large-scale contaminants:} Gaussian random maps with a red spectrum of the form $C_\ell\propto (\ell+1)^\beta$, where $\beta$ is a random number chosen within the range $\beta\in(-1,-3)$.
        \item {\bf Small-scale contaminants:} Gaussian random maps with a flat spectrum $C_\ell={\rm const.}$
      \end{itemize}
      In both cases we fixed the amplitude of the contaminant power spectrum such that it would yield a $10\%$ contamination in the data power spectrum at $\ell=400$. For spin-2 fields, we assumed the same power spectrum for $E$ and $B$ modes, with no cross-correlation between them. The resulting contaminant power spectra are shown in Figure \ref{fig:clcont}. When exploring the effects of mode deprojection, we generate 100 contaminant maps of both types and add them to each simulated realization. We then deproject the full set of 100 contaminant templates from the simulated maps and compute the corresponding unbiased power spectra. Note that our fiducial results do not include the effects of mode deprojection. These are discussed separately.

>>>>

    \subsection{Approximate covariances}\label{ssec:theory.approx}
      When presenting our results in Section \ref{sec:results}, we will compare the true covariance matrix, estimated from a large number of Gaussian simulations, with the analytical covariance estimated under different approximations. In descending order of complexity, these are:
      \begin{enumerate}
        \item The narrow-kernel approximation (labelled {\bf NKA} here), described in the previous sections. This approximation assumes that the support of the harmonic-space masks (represented by the mode-coupling coefficients in e.g. Eq. \ref{eq:mcms}) is small compared to the variation of the true power spectrum with $\ell$. Additionally, it neglects all derivatives of the sky mask when accounting for the spin nature of the fields involved.
        \item The {\bf spin-0} approximation corresponds to a simplified version of the NKA in which the spin nature of all fields involved is completely ignored, and all fields, including the $E$- and $B$-mode components of a spin-2 field, are treated as spin-0 quantities.
        \item The mode-counting approximation (labelled {\bf MC} here),
          commonly known as the {\sl Knox formula} \cite{1995PhRvD..52.4307K},
          which applies the result found for full-sky observations (Eq.
          \ref{eq:cov_naive}) to masked fields, corrected by an overall factor that accounts to the loss of modes due to the sky mask. In this case, the covariance is simply given by:
        \begin{equation}\label{eq:cov_naive_bpw}
          {\rm Cov}\left(C^{ab}_q,C^{cd}_{q'}\right)=\delta^K_{qq'}\frac{C^{ad}_qC^{bc}_q+C^{ac}_qC^{bd}_q}{(2\ell_q+1)\,f_{\rm sky}\,N_q},
        \end{equation}
        where $\ell_q$ is the mean multipole in the $q$-th bandpower, $N_q$ is the number of multipoles assigned to it, and $f_{\rm sky}$ is the available sky fraction.
      \end{enumerate}

@@

      We consider the case of auto- and cross-correlations between all fields
      in two redshift bins, with redshift distributions modelled as Gaussians
      with width $\sigma_z=0.13$ centered around redshifts $0.75$ and $0.95$,
      with number densities $n_\Omega=7.5\,{\rm arcmin}^{-2}$. The
      corresponding redshift distributions $p_z(z)$ are shown in Figure
      \ref{fig:pz}. For simplicity we use a constant bias $b(z)=1$. For these
      specifications, we generate signal power spectra using the Core
      Cosmology Library ({\tt CCL} \cite{2019ApJS..242....2C}) for
      cosmological parameters
      $(\Omega_c,\Omega_b,h,A_s,n_s)=(0.27,0.045,0.67,2.1\times10^{-9},0.96)$.
      The resulting non-zero signal and noise power spectra are shown in
      Figure~\ref{fig:cl-2bins}.

@@

      We have also explored the impact of the presence of sky contaminants on the estimate of the covariance matrix. As described in \cite{2019MNRAS.484.4127A}, the presence of a small contamination from observational systematics in the data can be accounted for through a technique known as {\sl mode deprojection} \cite{1992ApJ...398..169R,2004PhRvD..69l3003S,2017MNRAS.465.1847E}. In this method, the contamination is modeled as a linear contribution at the map level from contaminants with a known template. Mode deprojection then consists on projecting the data onto the subspace of modes that are perpendicular to those templates, effectively removing all modes from the map that ``look like'' any of the contaminants. This removal of modes has been shown to provide unbiased estimates of the power spectrum, however it could potentially affect the power spectrum uncertainties due to the loss of statistical power. To study this effect, we have also generated contaminant maps of two types:
      \begin{itemize}
        \item {\bf Large-scale contaminants:} Gaussian random maps with a red spectrum of the form $C_\ell\propto (\ell+1)^\beta$, where $\beta$ is a random number chosen within the range $\beta\in(-1,-3)$.
        \item {\bf Small-scale contaminants:} Gaussian random maps with a flat spectrum $C_\ell={\rm const.}$
      \end{itemize}
      In both cases, we fixed the amplitude of the contaminant power spectrum
      such that it would yield a $10\%$ contamination in the data power
      spectrum at $\ell=400$. For spin-2 fields, we assumed the same power
      spectrum for $E$ and $B$ modes, with no cross-correlation between them.
      The resulting contaminant power spectra are shown in Figure
      \ref{fig:clcont}. When exploring the effects of mode deprojection, we
      generated 100 contaminant maps of both types and added them to each
      simulated realization. We then deprojected the full set of 100
      contaminant templates from the simulated maps and computed the
      corresponding unbiased power spectra. Note that, in what follows, our
      fiducial results do not include the effects of mode deprojection. These
      are discussed separately.
